Topological Equivariant Artist Model

### 2022-03-02 slides/main.tex
code based slide hiding + reworked dfunc unpacking

\documentclass[xcolor={dvipsnames}, handout]{beamer}
%\documentclass[xcolor={dvipsnames}]{beamer}
\setbeamertemplate{footline}[frame number]
%\usepackage{amsmath,amsfonts,amssymb,pxfonts,eulervm,xspace}
\usepackage{amsmath, amsfonts, amssymb, mathtools, eulervm, xspace}
\renewcommand{\restriction}{\mathord{\upharpoonright}} %restriction w/p space
\usepackage{relsize}%mathlarger
\usepackage{bm}
\usepackage{centernot}
\usepackage{mathrsfs} % math script fonts
\usepackage{tikz}
\usetikzlibrary{cd} % commutative diagrams
\newtheorem{prop}{Proposition} %math?

@@

\usepackage{tabulary}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}

@@

\title{Topological Equivariant Artist Model}
\begin{comment}
\begin{frame}
	\titlepage
    Hannah Aizenman, Tom Caswell, Michael Grossberg\\
    %Committee: Dr. Robert Haralick, Dr. Lev Manovich, Dr. Huy Vo\\
    %External Member: Dr. Marcus Hanwell
\end{frame}

\section{Introduction}
\begin{frame}{What are we doing?}
    \begin{itemize}
        \item develop a model for describing data to graphic transformations
        \item specify a visualization library architecture based on this model
        \item implement functional(ish) components based on this model using ideas from functional programming
    \end{itemize}
\end{frame}

%% maybe pull out the middle for now? move the 3 stages down to construction? 
\begin{frame}{What do visualization libraries do?}
    \begin{figure}
        \begin{overprint}
            \onslide<1|handout:1>\includegraphics[width=\linewidth]{figures/flow/s2.png}
            \onslide<2|handout:2>\includegraphics[width=\linewidth]{figures/flow/s_vc.png}
            \onslide<3|handout:3>\includegraphics[width=\linewidth]{figures/flow/s_mark.png}
            \onslide<4|handout:4>\includegraphics[width=\linewidth]{figures/flow/s3.png}
        \end{overprint}
    \end{figure}
\end{frame}

\begin{frame}{Case Study: Matplotlib}
    \begin{figure}
       \includegraphics[width=\linewidth]{figures/flow/artists.png}
    \end{figure}
\end{frame}

\begin{frame}{Visualizations Preserve Structure}
    \begin{description}
        \item [continuity] topological properties \cite{wilkinsonGrammarGraphics2005}, i.e. how elements in a dataset are organized, e.g. discrete rows in a table, networked nodes, pixels in an image, points on a line
        \item [equivariance] data and visual encodings are matched such that transformations have an equivalent effect on data and graphical representations, e.g. rotating a matrix and image, shifting  points on a line and a line graphic
      \end{description}
\end{frame}

\begin{frame}{Continuity}
    \begin{figure}
        \includegraphics[width=\linewidth]{../paper/figures/k_different_types.png}
    \end{figure}
\end{frame}

\begin{frame}{Expressed in container}    
    \begin{figure}
        \includegraphics[width=1\textwidth]{figures/intro/munzner_datatypes.png}
        \caption{Figure 2.8 in Munzner's Visualization Analysis and Design\cite{munznerVisualizationAnalysisDesign2014}}
    \end{figure}
\end{frame}

\begin{frame}{Why is container type not enough?}
    \includegraphics[width=1\linewidth]{../paper/figures/whycontinuity.png}
\end{frame}

\begin{frame}{Equivariance}
    \begin{description}
        \item[Retinal Variables \& Marks] visual encodings should match properties of the data \cite{bertinSemiologyGraphicsDiagrams2011a}
        \pause
        \item[Graphical Integrity] graphs show \textbf{only} the data\cite{tufteVisualDisplayQuantitative2001}
        \pause 
        \item[Naturalness] easier to understand when properties match\cite{norman_things_smart}
        \pause
        \item[Expressiveness] which structure preserving mappings can a tool implement\cite{mackinlayAutomatingDesignGraphical1986}] 
    \end{description}
\end{frame}

%flip columns
\begin{frame}{Frameworks for Expressing Visual Equivariance}
    \begin{description}
        \item[linguistically] visualization has syntax, semantics, grammar expresses how to design structure preserving visualizations
        \cite{mackinlayAutomatingDesignGraphical1986,mackinlayAUTOMATICDESIGNGRAPHICAL1987,wilkinsonGrammarGraphics2005}

@@

\begin{frame}{Domain specific libraries know their structure\cite{HeerSoftware2006}}
    \begin{table}
        %\renewcommand{\arraystretch}{2}
        %
        \begin{tabular}{>{\onslide<1->}l>{\onslide<2->}l>{\onslide<3->}l}
            \includegraphics[width=.24\textwidth]{figures/intro/table.png} & \includegraphics[width=.3\textwidth]{figures/intro/landsat.png} & \includegraphics[width=.33\textwidth]{figures/math/graph.png} \\
            ggplot\cite{wickhamGgplot2ElegantGraphics2016a}  & ImageJ\cite{schneiderNIHImageImageJ2012}& Gephi\cite{bastianGephiOpenSource2009}\\
            Vega\cite{satyanarayanDeclarativeInteractionDesign2014} & ImagePlot\cite{studiesCulturevisImageplot2021} & Graphviz\cite{ellsonGraphvizOpenSource2002}\\
            Altair\cite{vanderplasAltairInteractiveStatistical2018}& Napari\cite{nicholas_sofroniew_2021_4533308} & Networkx\cite{HagbergExploringNetwork2008}\\
             Tableau \cite{StoltePolaris2002}& &\\
            \cite{hanrahanVizQL2006,MackinlayShowme2007}&&\\

        \end{tabular}
    \end{table}
\end{frame}

\begin{frame}{General purpose libraries generally can't\cite{toryRethinkingVisualizationHighlevel2004}}
    \begin{figure}
        \includegraphics[height=.3\textheight]{../paper/figures/k_different_types.png}
    \end{figure}
    \begin{enumerate}
        \item Matplotlib\cite{hunterMatplotlib2DGraphics2007} $\rightarrow$Seaborn\cite{waskom2020seaborn}, xarray \cite{hoyer2017xarray} 
        \item D3 \cite{bostockDataDrivenDocuments2011}
        \item VTK \cite{hanwellVisualizationToolkitVTK2015,geveciVTK2012}(MayaVi\cite{RamachandranMayaVI2011})$\rightarrow$ Titan\cite{brianwylieUnifiedToolkitInformation2009}, ParaView\cite{ahrens2005paraview}
    \end{enumerate}
\end{frame}
\end{comment}

\section{Algebraic Topology & Category Theory}

\begin{frame}{Mathematical Data Abstraction}
    \begin{description}
        \item[Fiber Bundles] "unified, dimension-independent framework" that expresses data as the mapping between continuity and fields \cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}
        \item[Category Theory Language] express constraints in specifications \cite{wielsManagementEvolvingSpecifications1998}   
        \item[Sheaves on Bundles] "algebraic data structure" for representing data over topological spaces \cite{ghristElementaryAppliedTopology2014}
    \end{description}
\end{frame}

@@

\begin{frame}

@@

        \begin{description}[style=nextline]

@@

\subsection{Category Theory Language}
\begin{frame}[fragile]{}
    \begin{minted}{python}
        Artist(data:Data) -> Graphic
    \end{minted}
\end{frame}

\begin{frame}{Category $\textcolor{source}{\mathcal{C}}$}
\begin{columns}
    \column{0.39\textwidth}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        \onslide*<1-|handout:1>{\textcolor{source}{C_1}} 
        \onslide*<3-|handout:1>{\arrow[r, "f", color=source]}
        \onslide*<4-|handout:1>{\arrow[rd, "g\circ f"', color=source]}
        \onslide*<2-|handout:1>{\arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source]} \& 
        \onslide*<1-|handout:1>{\textcolor{source}{C_2}}
        \onslide*<3-|handout:1>{\arrow[d, "g", color=source]} 
        \onslide*<2-|handout:1>{\arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source]} \\\& 
        \onslide*<1-|handout:1>{\textcolor{source}{C_3}}
        \onslide*<2-|handout:1>{\arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]}              
    \end{tikzcd}
    \end{equation*}
    \column{0.59\textwidth}
    \begin{alertblock}<5-|handout:1>{associativity} 
        if $f: C_1 \rightarrow C_2$, $g: C_2 \rightarrow C_3$ and $h: C_3 \rightarrow C_4$ then $h\circ (g \circ f) = (h \circ g) \circ f$
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity} 
        for every $f: C_1 \rightarrow C_2$ there exists identity morphisms $f \circ id_{C_1} = f = id_{C_2} \circ f$
    \end{alertblock}
    \end{columns}
\end{frame}

\begin{frame}{Opposite Category $\textcolor{source}{\mathcal{C}^{op}}$}
    \begin{columns}
        \column{0.49\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \textcolor{fade}{C_1} \arrow[r, "f", color=fade] \arrow[rd, "g\circ f"', color=fade] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=fade] \& \textcolor{fade}{C_2} \arrow[d, "g", color=fade] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=fade] \\
        \& \textcolor{fade}{C_3} \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=fade]              
        \end{tikzcd}
        \end{equation*}
        \column{0.49\textwidth}
        \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&]
            \textcolor{source}{C_1} \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source] \& \textcolor{source}{C_2} \arrow[l, "f"',color=source] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source]\\
            \& \textcolor{source}{C_3} \arrow[u, "g"', color=source] \arrow[lu, "f \circ g", color=source] \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]
            \end{tikzcd}
        \end{equation*}
        \end{columns}
\end{frame}

\begin{frame}{Functor $\textcolor{functor}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$}
\begin{columns}
    \column{.39\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, ]
            \onslide*<1-|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-|handout:1>{\arrow[d, "f"', shift right=0, color=source]} 
            \onslide*<3-|handout:1>{\arrow[r, "F", color=functor, maps to]} \& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c)}} 
            \onslide*<0|handout:1>{\textcolor{target}{F(c)=d}} 
            \onslide*<2|handout:0>{\arrow[d, shift right=0, color=target]}
            \onslide*<3-|handout:0>{\arrow[d, "F(f)", shift right=0, color=target]}
            \onslide*<0|handout:1>{\arrow[d, "F(f)", shift right=3, color=target]} \\
            \onslide*<1-|handout:1>{\textcolor{source}{c^{\prime}}} 
            \onslide*<3-|handout:1>{\arrow[r, "F"', color=functor, maps to]}\& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d^{\prime}}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c^{\prime})}}
            \onslide*<0|handout:1>{\textcolor{target}{F(c^{\prime})= d^{\prime}}}                    
        \end{tikzcd}
    \end{equation*}
    \column{.59\textwidth}
    \begin{alertblock}<5-|handout:1>{composition}
        \begin{align*}
            \textcolor{functor}{F}(\textcolor{source}{g}) \circ  \textcolor{functor}{F}(\textcolor{source}{f}) = \textcolor{functor}{F} (\textcolor{source}{g}\circ \textcolor{source}{f})
        \end{align*}
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity}
        \begin{align*}
            \textcolor{functor}{F}(\textcolor{source}{id_c}) = \textcolor{target}{id}_{\textcolor{functor}{F}(\textcolor{source}{c})}
        \end{align*}
    \end{alertblock}
\end{columns}
\end{frame}

\subsubsection{Natural Transforms}
\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \onslide<|handout:1>{
    \adjustbox{scale=3, center}{
        \begin{tikzcd}[ampersand replacement=\&]
            \& {} \arrow[dd, "\alpha" , Rightarrow, shorten=1.5em, color=nattran] \&             \\
          \textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor, maps to] \arrow[rr, "G"', bend right, color=functor, maps to] \& \& \textcolor{target}{\mathcal{D}} \\
            \& {} \&            
          \end{tikzcd}}}
\end{frame}

\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \begin{equation*}
        \begin{tikzcd}[column sep=huge, ampersand replacement = \&]
            \onslide*<2-|handout:1>{\textcolor{target}{F(c)}}
            \onslide*<2-|handout:1>{\arrow[dd, "F(f)"', color=target]}
            \onslide*<4-5|handout:1>{\arrow[rr, "\alpha_{c}", bend left, color=nattran, Rightarrow]}  
            \onslide*<6|handout:0>{\arrow[rr, "\alpha_{c}", color=nattran, Rightarrow]} \& 
            \onslide*<1-4|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-4|handout:1>{\arrow[dd, "f" description, color=source]}
            \onslide*<3-4|handout:1>{\arrow[r, "G"', color=functor,maps to ]}
            \onslide*<2-4|handout:1>{\arrow[l, "F", color=functor, maps to]} \& 
            \onslide*<3-|handout:1>{\textcolor{target}{G(c)}} 
            \onslide*<3-|handout:1>{\arrow[dd, "G(f)", color=target, maps to]} \\
            {} 
            \onslide*<4|handout:1>{\arrow[rr, dotted, color=nattran, Rightarrow]}
            \onslide*<5|handout:0>{\arrow[rr, color=nattran, Rightarrow]} \& \& {}                      \\
            \onslide*<2-|handout:1>{\textcolor{target}{F(c^{\prime})}} 
            \onslide*<4-5|handout:1>{\arrow[rr, "\alpha_{c^{\prime}}"', bend right, color=nattran, Rightarrow]} 
            \onslide*<4-5|handout:0>{\arrow[rr, "\alpha_{c^{\prime}}"', color=nattran, maps to]}\& 
            \onslide*<1-4|handout:1>{\textcolor{source}{c^{\prime}}}
            \onslide*<2-4|handout:1>{\arrow[l, "F"', color=functor, maps to]} 
            \onslide*<3-4|handout:1>{\arrow[r, "G", color=functor, maps to]} \& 
            \onslide*<3-|handout:1>{\textcolor{target}{G(c^{\prime})}}          
        \end{tikzcd}
    \end{equation*}
\end{frame}

@@

\begin{frame}{Sheaves on Bundles}
    A sheaf is a presheaf that satisfies the following two axioms\cite{bakerMathsSheaf}\\
    \begin{block}<2-|handout:1>{locality}
        \onslide<3-|handout:1>{
        given $\opensetc = \bigcup\limits_{i\in I} \opensetc_i$ and $\dsectionc^{a}, \dsectionc^{b} \in \sheafc(\opensetc)$,}
        \onslide<4|handout:1>{\\
        if $\dsectionc^{a}\restriction_{\opensetc_i} = \dsectionc^{b}\restriction_{\opensetc_i}$ for each $\opensetc_i \in \opensetc$}
        \onslide<4|handout:1>{then $\dsectionc^{a} = \dsectionc^{b}$}
    \end{block} 
    \begin{block}<5-|handout:1>{gluing} 
         given $\dsectionc^{i} \in \sheafc(\opensetc_i)$
        \onslide<6-|handout:1>{s.t. ${\dsectionc^{i}}\restriction_{\opensetc_i\cap \opensetc_j} = {\dsectionc^{j}}\restriction_{\opensetc_i \cap \opensetc_j}$ for $\opensetc_i, \opensetc_j \in \opensetc$,}
        \onslide<7-|handout:1>{\\there exists $\dsectionc \in \sheafc(\opensetc)$ such that $\dsectionc\restriction_{\opensetc_i} = {\dsectionc^{i}}$} 
    \end{block}      
\end{frame}

@@

\begin{frame}{}

@@

            \onslide*<0|handout:2->{\opensetgc}

@@

\begin{frame}{Example: Scatter Plot}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_scatter.png}
    \end{figure}
\end{frame}

>>>>

\documentclass[xcolor={dvipsnames}, handout]{beamer}
%\documentclass[xcolor={dvipsnames}]{beamer}
\setbeamertemplate{footline}[frame number]
\setbeamersize{description width=-\labelsep}

%\usepackage{amsmath,amsfonts,amssymb,pxfonts,eulervm,xspace}
\usepackage{amsmath, amsfonts, amssymb, mathtools, eulervm, xspace}
\renewcommand{\restriction}{\mathord{\upharpoonright}} %restriction w/p space
\usepackage{relsize} %mathlarger
\usepackage{bm}
\usepackage{centernot}
\usepackage{mathrsfs} % math script fonts
\usepackage{tikz}
\usetikzlibrary{cd} % commutative diagrams
\newtheorem{prop}{Proposition} %math?

@@

\usepackage{tabulary}
\usepackage{tabularx}
%\usepackage{enumitem} $ won't work with beamer
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}

@@

\title{Topological Equivariant Artist Model}

\begin{frame}<presentation:1|handout:1>
	\titlepage
    Hannah Aizenman, Tom Caswell, Michael Grossberg\\
    %Committee: Dr. Robert Haralick, Dr. Lev Manovich, Dr. Huy Vo\\
    %External Member: Dr. Marcus Hanwell
\end{frame}

\section{Introduction}
\begin{frame}<presentation:1|handout:0>{What are we doing?}
    \begin{itemize}
        \item develop a model for describing data to graphic transformations
        \item specify a visualization library architecture based on this model
        \item implement functional(ish) components based on this model using ideas from functional programming
    \end{itemize}
\end{frame}

%% maybe pull out the middle for now? move the 3 stages down to construction? 
\begin{frame}<presentation:1|handout:0>{What do visualization libraries do?}
    \begin{figure}
        \begin{overprint}
            \onslide<1|handout:1>\includegraphics[width=\linewidth]{figures/flow/s2.png}
            \onslide<2|handout:2>\includegraphics[width=\linewidth]{figures/flow/s_vc.png}
            \onslide<3|handout:3>\includegraphics[width=\linewidth]{figures/flow/s_mark.png}
            \onslide<4|handout:4>\includegraphics[width=\linewidth]{figures/flow/s3.png}
        \end{overprint}
    \end{figure}
\end{frame}

\begin{frame}<presentation:1|handout:0>{Case Study: Matplotlib}
    \begin{figure}
       \includegraphics[width=\linewidth]{figures/flow/artists.png}
    \end{figure}
\end{frame}

\begin{frame}<presentation:1|handout:0>{Visualizations Preserve Structure}
    \begin{description}
        \item [continuity] topological properties \cite{wilkinsonGrammarGraphics2005}, i.e. how elements in a dataset are organized, e.g. discrete rows in a table, networked nodes, pixels in an image, points on a line
        \item [equivariance] data and visual encodings are matched such that transformations have an equivalent effect on data and graphical representations, e.g. rotating a matrix and image, shifting  points on a line and a line graphic
      \end{description}
\end{frame}

\begin{frame}<presentation:1|handout:0>{Continuity}
    \begin{figure}
        \includegraphics[width=\linewidth]{../paper/figures/k_different_types.png}
    \end{figure}
\end{frame}

\begin{frame}<presentation:1|handout:0>{Expressed in container} 
    \begin{figure}
        \includegraphics[width=1\textwidth]{figures/intro/munzner_datatypes.png}
        \caption{Figure 2.8 in Munzner's Visualization Analysis and Design\cite{munznerVisualizationAnalysisDesign2014}}
    \end{figure}
\end{frame}

\begin{frame}<presentation:1|handout:0>{Why is container type not enough?}
    \includegraphics[width=1\linewidth]{../paper/figures/whycontinuity.png}
\end{frame}

\begin{frame}<presentation:1|handout:0>{Equivariance}
    \begin{description}
        \item[Retinal Variables \& Marks] visual encodings should match properties of the data \cite{bertinSemiologyGraphicsDiagrams2011a}
        \pause
        \item[Graphical Integrity] graphs show \textbf{only} the data\cite{tufteVisualDisplayQuantitative2001}
        \pause 
        \item[Naturalness] easier to understand when properties match\cite{norman_things_smart}
        \pause
        \item[Expressiveness] which structure preserving mappings can a tool implement\cite{mackinlayAutomatingDesignGraphical1986}] 
    \end{description}
\end{frame}

%flip columns
\begin{frame}<presentation:1|handout:0>{Frameworks for Expressing Visual Equivariance}
    \begin{description}
        \item[linguistically] visualization has syntax, semantics, grammar expresses how to design structure preserving visualizations
        \cite{mackinlayAutomatingDesignGraphical1986,mackinlayAUTOMATICDESIGNGRAPHICAL1987,wilkinsonGrammarGraphics2005}

@@

\begin{frame}<presentation:1|handout:0>
    \frametitle{Domain specific libraries know their structure\cite{HeerSoftware2006}}
    \begin{table}
        %\renewcommand{\arraystretch}{2}
        %
        \begin{tabular}{>{\onslide<1->}l>{\onslide<2->}l>{\onslide<3->}l}
            \includegraphics[width=.24\textwidth]{figures/intro/table.png} & \includegraphics[width=.3\textwidth]{figures/intro/landsat.png} & \includegraphics[width=.33\textwidth]{figures/math/graph.png} \\
            ggplot\cite{wickhamGgplot2ElegantGraphics2016a}  & ImageJ\cite{schneiderNIHImageImageJ2012}& Gephi\cite{bastianGephiOpenSource2009}\\
            Vega\cite{satyanarayanDeclarativeInteractionDesign2014} & ImagePlot\cite{studiesCulturevisImageplot2021} & Graphviz\cite{ellsonGraphvizOpenSource2002}\\
            Altair\cite{vanderplasAltairInteractiveStatistical2018}& Napari\cite{nicholas_sofroniew_2021_4533308} & Networkx\cite{HagbergExploringNetwork2008}\\
             Tableau \cite{StoltePolaris2002}& &\\
            \cite{hanrahanVizQL2006,MackinlayShowme2007}&&\\        
        \end{tabular}
    \end{table}
\end{frame}

\begin{frame}<presentation:1|handout:0>
    \frametitle{General purpose libraries generally can't\cite{toryRethinkingVisualizationHighlevel2004}}
    \begin{figure}
        \includegraphics[height=.3\textheight]{../paper/figures/k_different_types.png}
    \end{figure}

    \begin{enumerate}
        \item Matplotlib\cite{hunterMatplotlib2DGraphics2007} $\rightarrow$ Seaborn\cite{waskom2020seaborn}, xarray \cite{hoyer2017xarray} 
        \item D3 \cite{bostockDataDrivenDocuments2011}
        \item VTK \cite{hanwellVisualizationToolkitVTK2015,geveciVTK2012},MayaVi\cite{RamachandranMayaVI2011}$\rightarrow$ Titan\cite{brianwylieUnifiedToolkitInformation2009}, ParaView\cite{ahrens2005paraview}
    \end{enumerate}
\end{frame}

\section{Algebraic Topology & Category Theory}
\begin{frame}<presentation:1|handout:0>{Mathematical Data Abstraction}
    \begin{description}
        \item[Fiber Bundles] "unified, dimension-independent framework" that expresses data as the mapping between continuity and fields \cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}
        \item[Category Theory Language] express constraints in specifications \cite{wielsManagementEvolvingSpecifications1998}   
        \item[Sheaves on Bundles] "algebraic data structure" for representing data over topological spaces \cite{ghristElementaryAppliedTopology2014}
    \end{description}
\end{frame}

@@

\begin{frame}<presentation:1|handout:0>

@@

        \begin{description}

@@

\subsection{Category Theory Language}
\begin{frame}<presentation:1|handout:0>[fragile]{}
    \begin{minted}{python}
        Artist(data:Data) -> Graphic
    \end{minted}
\end{frame}

\begin{frame}<presentation:1|handout:0>{Category $\textcolor{source}{\mathcal{C}}$}
\begin{columns}
    \column{0.39\textwidth}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        \onslide*<1-|handout:1>{\textcolor{source}{C_1}} 
        \onslide*<3-|handout:1>{\arrow[r, "f", color=source]}
        \onslide*<4-|handout:1>{\arrow[rd, "g\circ f"', color=source]}
        \onslide*<2-|handout:1>{\arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source]} \& 
        \onslide*<1-|handout:1>{\textcolor{source}{C_2}}
        \onslide*<3-|handout:1>{\arrow[d, "g", color=source]} 
        \onslide*<2-|handout:1>{\arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source]} \\\& 
        \onslide*<1-|handout:1>{\textcolor{source}{C_3}}
        \onslide*<2-|handout:1>{\arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]}              
    \end{tikzcd}
    \end{equation*}
    \column{0.59\textwidth}
    \begin{alertblock}<5-|handout:1>{associativity} 
        if $f: C_1 \rightarrow C_2$, $g: C_2 \rightarrow C_3$ and $h: C_3 \rightarrow C_4$ then $h\circ (g \circ f) = (h \circ g) \circ f$
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity} 
        for every $f: C_1 \rightarrow C_2$ there exists identity morphisms $f \circ id_{C_1} = f = id_{C_2} \circ f$
    \end{alertblock}
    \end{columns}
\end{frame}

\begin{frame}<presentation:1|handout:0>{Opposite Category $\textcolor{source}{\mathcal{C}^{op}}$}
    \begin{columns}
        \column{0.49\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \textcolor{fade}{C_1} \arrow[r, "f", color=fade] \arrow[rd, "g\circ f"', color=fade] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=fade] \& \textcolor{fade}{C_2} \arrow[d, "g", color=fade] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=fade] \\
        \& \textcolor{fade}{C_3} \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=fade]              
        \end{tikzcd}
        \end{equation*}
        \column{0.49\textwidth}
        \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&]
            \textcolor{source}{C_1} \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source] \& \textcolor{source}{C_2} \arrow[l, "f"',color=source] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source]\\
            \& \textcolor{source}{C_3} \arrow[u, "g"', color=source] \arrow[lu, "f \circ g", color=source] \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]
            \end{tikzcd}
        \end{equation*}
        \end{columns}
\end{frame}

\begin{frame}<presentation:1|handout:0>
    \frametitle{Functor $\textcolor{functor}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$}
\begin{columns}
    \column{.39\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, ]
            \onslide*<1-|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-|handout:1>{\arrow[d, "f"', shift right=0, color=source]} 
            \onslide*<3-|handout:1>{\arrow[r, "F", color=functor, maps to]} \& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c)}} 
            \onslide*<0|handout:1>{\textcolor{target}{F(c)=d}} 
            \onslide*<2|handout:0>{\arrow[d, shift right=0, color=target]}
            \onslide*<3-|handout:0>{\arrow[d, "F(f)", shift right=0, color=target]}
            \onslide*<0|handout:1>{\arrow[d, "F(f)", shift right=3, color=target]} \\
            \onslide*<1-|handout:1>{\textcolor{source}{c^{\prime}}} 
            \onslide*<3-|handout:1>{\arrow[r, "F"', color=functor, maps to]}\& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d^{\prime}}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c^{\prime})}}
            \onslide*<0|handout:1>{\textcolor{target}{F(c^{\prime})= d^{\prime}}}                    
        \end{tikzcd}
    \end{equation*}
    \column{.59\textwidth}
    \begin{alertblock}<5-|handout:1>{composition}
        \begin{align*}
            \textcolor{functor}{F}(\textcolor{source}{g}) \circ  \textcolor{functor}{F}(\textcolor{source}{f}) = \textcolor{functor}{F} (\textcolor{source}{g}\circ \textcolor{source}{f})
        \end{align*}
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity}
        \begin{align*}
            \textcolor{functor}{F}(\textcolor{source}{id_c}) = \textcolor{target}{id}_{\textcolor{functor}{F}(\textcolor{source}{c})}
        \end{align*}
    \end{alertblock}
\end{columns}
\end{frame}

\subsubsection{Natural Transforms}
\begin{frame}<presentation:1|handout:0>
    \frametitle{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \onslide<|handout:1>{
    \adjustbox{scale=3, center}{
        \begin{tikzcd}[ampersand replacement=\&]
            \& {} \arrow[dd, "\alpha" , Rightarrow, shorten=1.5em, color=nattran] \&             \\
          \textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor, maps to] \arrow[rr, "G"', bend right, color=functor, maps to] \& \& \textcolor{target}{\mathcal{D}} \\
            \& {} \&            
          \end{tikzcd}}}
\end{frame}

\begin{frame}<presentation:1|handout:0>
    \frametitle{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \begin{equation*}
        \begin{tikzcd}[column sep=huge, ampersand replacement = \&]
            \onslide*<2-|handout:1>{\textcolor{target}{F(c)}}
            \onslide*<2-|handout:1>{\arrow[dd, "F(f)"', color=target]}
            \onslide*<4-5|handout:1>{\arrow[rr, "\alpha_{c}", bend left, color=nattran, Rightarrow]}  
            \onslide*<6|handout:0>{\arrow[rr, "\alpha_{c}", color=nattran, Rightarrow]} \& 
            \onslide*<1-4|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-4|handout:1>{\arrow[dd, "f" description, color=source]}
            \onslide*<3-4|handout:1>{\arrow[r, "G"', color=functor,maps to ]}
            \onslide*<2-4|handout:1>{\arrow[l, "F", color=functor, maps to]} \& 
            \onslide*<3-|handout:1>{\textcolor{target}{G(c)}} 
            \onslide*<3-|handout:1>{\arrow[dd, "G(f)", color=target, maps to]} \\
            {} 
            \onslide*<4|handout:1>{\arrow[rr, dotted, color=nattran, Rightarrow]}
            \onslide*<5|handout:0>{\arrow[rr, color=nattran, Rightarrow]} \& \& {}                      \\
            \onslide*<2-|handout:1>{\textcolor{target}{F(c^{\prime})}} 
            \onslide*<4-5|handout:1>{\arrow[rr, "\alpha_{c^{\prime}}"', bend right, color=nattran, Rightarrow]} 
            \onslide*<4-5|handout:0>{\arrow[rr, "\alpha_{c^{\prime}}"', color=nattran, maps to]}\& 
            \onslide*<1-4|handout:1>{\textcolor{source}{c^{\prime}}}
            \onslide*<2-4|handout:1>{\arrow[l, "F"', color=functor, maps to]} 
            \onslide*<3-4|handout:1>{\arrow[r, "G", color=functor, maps to]} \& 
            \onslide*<3-|handout:1>{\textcolor{target}{G(c^{\prime})}}          
        \end{tikzcd}
    \end{equation*}
\end{frame}

@@

\begin{frame}<presentation:1|handout:0>{Sheaves on Bundles}
    A sheaf is a presheaf that satisfies the following two axioms\cite{bakerMathsSheaf}\\
    \begin{block}<2-|handout:1>{locality}
        \onslide<3-|handout:1>{
        given $\opensetc = \bigcup\limits_{i\in I} \opensetc_i$ and $\dsectionc^{a}, \dsectionc^{b} \in \sheafc(\opensetc)$,}
        \onslide<4|handout:1>{\\
        if $\dsectionc^{a}\restriction_{\opensetc_i} = \dsectionc^{b}\restriction_{\opensetc_i}$ for each $\opensetc_i \in \opensetc$}
        \onslide<4|handout:1>{then $\dsectionc^{a} = \dsectionc^{b}$}
    \end{block} 
    \begin{block}<5-|handout:1>{gluing} 
         given $\dsectionc^{i} \in \sheafc(\opensetc_i)$
        \onslide<6-|handout:1>{s.t. ${\dsectionc^{i}}\restriction_{\opensetc_i\cap \opensetc_j} = {\dsectionc^{j}}\restriction_{\opensetc_i \cap \opensetc_j}$ for $\opensetc_i, \opensetc_j \in \opensetc$,}
        \onslide<7-|handout:1>{\\there exists $\dsectionc \in \sheafc(\opensetc)$ such that $\dsectionc\restriction_{\opensetc_i} = {\dsectionc^{i}}$} 
    \end{block}      
\end{frame}

@@

\begin{frame}<presentation:1|handout:1->{}

@@

            \onslide*<0|handout:2,4->{\opensetgc}
            \onslide*<0|handout:3>{\underbrace{\opensetc\times[0,1]^{m}}_{\opensetgc}}

@@

\begin{frame}<presentation:1|handout:0>{Example: Scatter Plot}
    \begin{figure}
        \includegraphics[scale=.1]{figures/math/push_pull_scatter.png}
    \end{figure}
\end{frame}
